\documentclass[11pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\scshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Seth Watts - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Seth Watts:  CV (Curriculum Vitae)},
            pdfauthor={Seth Watts},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% Make AP style (kinda) dates for the updated/today field

\usepackage{datetime}
\newdateformat{apstylekinda}{%
  \shortmonthname[\THEMONTH]. \THEDAY, \THEYEAR}

\begin{document}


\centerline{\huge \bf Seth Watts}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Doctoral student}
\moveleft.5\hoffset\centerline{School of Criminology and Criminal
Justice, Arizona State University}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:swatts12@asu.edu}{\nolinkurl{swatts12@asu.edu}}} \hspace{1 mm}      \faGlobe \hspace{1 mm} \href{http://\url{https://sbwatts.quarto.pub/sbw/}}{\tt \url{https://sbwatts.quarto.pub/sbw/}}    | \emph{Updated:} \apstylekinda\today} 

\vspace{2 mm}

\hrule


\pagestyle{plain}
\vspace{4mm}

\hypertarget{education}{%
\section{Education}\label{education}}

\emph{Arizona State University}

PhD, Criminology and Criminal Justice \hfill Expected 2024

Certificate,
\href{https://degrees.apps.asu.edu/masters-phd/major/ASU00/LASSRMGRCT/social-science-research-methods-graduate-certificate}{Social
Science Research Methods}

MS, Criminology and Criminal Justice \hfill 2019-2021

\emph{Bowling Green State University}

BA, Psychology \hfill 2015-2019

\vspace{2mm}

\hypertarget{research-interests}{%
\section{Research Interests}\label{research-interests}}

Policing, Public health, Program evaluation

\vspace{2mm}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{peer-reviewed}{%
\subsection{Peer-Reviewed}\label{peer-reviewed}}

White, M. D., Monk, K., \textbf{Watts, S}. (2023). A Half-Century
Investigation of Police Officer Line-of-Duty Deaths: Putting Recent
Trends in Long-Term Context. \emph{Police Practice and Research}, 1-18.
(\href{https://www-tandfonline-com.ezproxy1.lib.asu.edu/doi/abs/10.1080/15614263.2023.2267728}{DOI})

White, M. D., Orosco, C., \textbf{Watts, S}. (2023) Beyond Force and
Injuries: Examining Alternative (and Important) Outcomes for Police
De-escalation Training. \emph{Journal of Criminal Justice}, 89, 102129.
(\href{https://www-sciencedirect-com.ezproxy1.lib.asu.edu/science/article/pii/S0047235223001009?casa_token=OxErc72pD-QAAAAA:XATyRNg9im-Y4tSAmatE2RofJft49bpMx7c4_fOCiLyqIILE_rMDU03IA2yVHSmdepnLIrpzNfw}{DOI})

White, D. M., Orosco, C., \textbf{Watts, S}. (2023). Can De-escalation
Training Reduce Use of Force and Citizen Injury Without Compromising
Officer Safety? \emph{Journal of Experimental Criminology}, 1-26.
(\href{https://link-springer-com.ezproxy1.lib.asu.edu/article/10.1007/s11292-023-09584-8}{DOI})

White, M. D., \textbf{Watts, S}., Orosco, C., Malm, A., Perrone, D.
(2022). Leveraging Body-Worn Camera Footage to Better Understand Opioid
Overdoses and the Impact of Police-Led Naloxone Programs. \emph{American
Journal of Public Health}, \emph{112}(9), 1326-1332.
(\href{https://ajph.aphapublications.org/doi/abs/10.2105/AJPH.2022.306918}{DOI})

Gaub, J., White, M., Malm, A., \textbf{Watts, S}., Brown, K. (2022).
Investigation the Role and Utility of Body-Worn Cameras at the ``George
Floyd'' Protests. \emph{Policing: An International Journal},
\emph{45}(4), 633-647.
(\href{https://www.emerald.com/insight/content/doi/10.1108/PIJPSM-10-2021-0151/full/html}{DOI})

White, M. D., Perrone, D., \textbf{Watts, S}., Malm, A. (2021). Moving
Beyond Narcan: A Police, Social Service, and Researcher Collaborative
Response to the Opioid Crisis. \emph{American Journal of Criminal
Justice}, \emph{46}(4), 626-643.
(\href{https://link-springer-com.ezproxy1.lib.asu.edu/article/10.1007/s12103-021-09625-w}{DOI})

White, M. D., Malm, A., Perrone, D., \textbf{Watts, S}. (2021). Narcan
Cops: Officer Perceptions of Opioid Use and Willingness to Carry
Naloxone. \emph{Journal of Criminal Justice}, 72, 101778.
(\href{https://www-sciencedirect-com.ezproxy1.lib.asu.edu/science/article/pii/S0047235220302725?casa_token=M3KzLm4DIoUAAAAA:KhQQ6E6WpFcNQdyfTN33-SRHRPttqc81ijlWaNX0wOOYu3TiHBIa17DzDZS2_7K_vU9_CQwdAaA}{DOI})

\vspace{2mm}

\hypertarget{working-papers}{%
\subsection{Working Papers}\label{working-papers}}

\hypertarget{under-review}{%
\subsubsection{Under Review}\label{under-review}}

Brown, K., \textbf{Watts, S}., Turner, P., \& Wallace, D. How Does
Proximity to Service Providers Impact Punitivity in Stop Outcomes for
Individuals Experiencing Homelessness?

\hypertarget{in-progress}{%
\subsubsection{In Progress}\label{in-progress}}

\textbf{Watts, S}., White, M. D., Malm, A., Perrone, D. The Durability
of Police Officers' Attitudes about Naloxone and Opioid Overdose
Response: `Narcan Cops' Revisited.

\textbf{Watts, S}. LEO Liability When Administering Naloxone.

\vspace{2mm}

\hypertarget{technical-reports}{%
\subsection{Technical Reports}\label{technical-reports}}

\textbf{Watts, S}., White, M. D., Malm, A., Perrone, D. (2023) The Tempe
First-Responder Opioid Recovery Project, Year 4 Interim Evaluation
Report. \emph{Substance Abuse and Mental Health Services
Administration}.

\textbf{Watts, S}., White, M. D., Malm, A., Perrone, D. (2022) The Tempe
First-Responder Opioid Recovery Project, Year 3 Interim Evaluation
Report. \emph{Substance Abuse and Mental Health Services
Administration}.

White, M. D., \textbf{Watts, S}., Malm, A., Perrone, D. (2021) The Tempe
First-Responder Opioid Recovery Project, Year 2 Interim Evaluation
Report. \emph{Substance Abuse and Mental Health Services
Administration}.

White, M. D., \textbf{Watts, S}., Malm, A., Perrone, D. (2020) The Tempe
First-Responder Opioid Recovery Project, Year 1 Interim Evaluation
Report. \emph{Substance Abuse and Mental Health Services
Administration}.

\vspace{2mm}

\hypertarget{professional-experience}{%
\section{Professional Experience}\label{professional-experience}}

Graduate Research Assistant \hfill 2020-

A Process and Outcome Evaluation of Truleo's Automated Body-Worn Camera
Review Technology in Three Arizona Police Departments. Funded by: Arnold
Ventures. 2024 - 2025 (\$501,238). Supervisor: Dr.~Michael D. White

The Effect of Automated Body-Camera Review on Officers' Professionalism
and Behavioral Outcomes. Funded by: Arnold Ventures. June -- December
2023 (\$99,980; planning grant). Supervisor: Dr.~Michael D. White

The Tempe First-Responder Opioid Recovery Project Center for Violence
Prevention and Community Safety, School of Criminology and Criminal
Justice, Arizona State University. Funded by: Substance Abuse and Mental
Health Services administration. 2020 -- 2023 (\$400,000). Supervisor:
Dr.~Michael D. White

Technical Assistance Provider for the National Body-Worn Camera Pilot
Implementation Program Center for Violence Prevention and Community
Safety, School of Criminology and Criminal Justice, Arizona State
University. Funded by: Bureau of Justice Assistance. 2020 -- 2022
(\$800,000). Supervisor: Dr.~Michael D. White

\vspace{2mm}

Graduate Service Assistant \hfill 2019

Arizona State University, School of Criminology and Criminal Justice
Supervisor: Dr.~Cody Telep

\vspace{2mm}

\hypertarget{media}{%
\section{Media}\label{media}}

Crime and Justice News
(\href{https://www.ncja.org/crimeandjusticenews/research-backs-police-response-to-drug-overdoses}{Sep,
16, 2022}), Public Health Post
(\href{https://www.publichealthpost.org/research/tempe-opioid-recovery/}{Sep,
16, 2021})

\vspace{2mm}

\hypertarget{conference-presentations}{%
\subsection[Conference Presentations]{\texorpdfstring{Conference
Presentations\footnote{Presented by coauthor (\(P\))}}{Conference Presentations}}\label{conference-presentations}}

Gutierrez, S., Mathis, S., Sanuth, A., Watts, S., Wallace, D. (February
2024). Is Law-Violating Driving Behavior Race Specific? Mapping Rates of
At-Fault Traffic Accidents by Race. Western Society of
Criminology.\(^P\)

Watts, S., White, M. D., Malm, A., Perrone, D. (November 2023).The
Durability of Police Officers' Attitudes about Naloxone and Opioid
Overdose Response: `Narcan Cops' Revisited. American Society of
Criminology.

Watts, S., White, M. D., Malm, A., Perrone, D. (November 2022). The
Tempe First Responder Opioid Recovery Project. American Society of
Criminology.

White, M. D., Watts, S., Orosco, C., Malm, A., Perrone, D (March 2022).
Myth busting Police-Led Naloxone Programs with Body-Worn Camera Footage.
Academy of Criminal Justice Sciences.

White, M. D., Orosco, C. A., Watts, S., Malm, A., Perrone, D (2020). The
Tempe First Responder Opioid Recovery Project. Southern Criminal Justice
Association.\(^P\)

\vspace{2mm}

\hypertarget{other-presentations}{%
\subsection{Other Presentations}\label{other-presentations}}

White, M. D., Watts, S. (2024). Making the Invisible Visible: Body-Worn
Cameras as a Tool for Uncovering Bad (and Good) Policing. ASU CCJ
Colloquium Series.

\vspace{2mm}

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\emph{Arizona State University}

\hypertarget{instructor}{%
\subsection{Instructor}\label{instructor}}

CRJ: 201 Crime Control Policies (Online) \hfill Summer 2023

CRJ: 303 Statistical Analyses (Online) \hfill Summer 2023

CRJ: 100 Introduction to Criminal Justice (Online) \hfill Summer 2022

CRJ: 302 Research Methods (Online) \hfill Summer 2022

\vspace{2mm}

\hypertarget{teaching-assistant}{%
\subsection{Teaching Assistant}\label{teaching-assistant}}

CRJ: 230 Introduction to Policing (Online) \hfill Spring 2023

CRJ: 409 Police Accountability \hfill Spring 2023

CRJ: 230 Introduction to Policing (Online) \hfill Spring 2020

CRJ: 230 Introduction to Policing (Online) \hfill Fall 2019

CRJ: 240 Introduction to Corrections (Online) \hfill Fall 2019

\vspace{2mm}

\hypertarget{activities-and-service}{%
\section{Activities and Service}\label{activities-and-service}}

\hypertarget{conferences-attended}{%
\subsection{Conferences Attended}\label{conferences-attended}}

American Society of Criminology. Philadelphia, Pennsylvania \hfill 2023

American Society of Criminology. Atlanta, Georgia \hfill 2022

Academy of Criminal Justice Sciences. Las Vegas, Nevada \hfill 2022

Center for Undergraduate Research Symposium. Bowling Green, Ohio
\hfill 2019

\vspace{2mm}

\hypertarget{manuscript-reviews}{%
\subsection{Manuscript Reviews}\label{manuscript-reviews}}

\emph{Journal of Drug Issues}

\emph{Journal of Harm Reduction}

\emph{Police Practice and Research: An International Journal}

\vspace{2mm}

\hypertarget{professional-development}{%
\subsection{Professional Development}\label{professional-development}}

\emph{Arizona State University} \hfill 2020-

\hypertarget{workshops}{%
\subsubsection{Workshops}\label{workshops}}

\href{https://sites.google.com/view/simdworkshop/home}{Statistics,
Interpretation, Methods, and Data Workshop},
\href{https://jacobtnyoung.github.io/RWorkshop/}{R Workshop}, Teaching
Portfolio Development, Classroom Management and Student Engagement,
Creating a Syllabus, Developing a CV/Cover Letter/Research Proposal,
Preparing for the Academic Job Market, Overview of Teaching Policies,
Writing Advice, Peer-Review Process, Conference Presentations,
Organizing and Planning your Career, Academic Writing and Publishing

\vspace{2mm}

\hypertarget{service-to-the-university}{%
\subsection{Service to the University}\label{service-to-the-university}}

\emph{Arizona State University} \hfill 2021-

Peer Mentorship Program (for first year PhD students), Peer Mentorship
Program (for MS students), Reviewer - MS Student's Application Material
for PhD Programs

\hypertarget{service-to-the-community}{%
\subsection{Service to the Community}\label{service-to-the-community}}

Volunteer in Policing (VIP) Tempe Police Department \hfill 2021-

\vspace{2mm}

\hypertarget{professional-affiliations}{%
\section{Professional Affiliations}\label{professional-affiliations}}

American Society of Criminology

Western Society of Criminology

\vspace{2mm}

\hypertarget{references}{%
\section{References}\label{references}}

Available upon request.

\end{document}
